<html>
<style>
table
{
  border-collapse: separate;
  border-spacing: 1em 0.5em;
  background-color: #ddd;
  color: #000;
}
</style>
<div align="center">
<h1>Proof of Concept</h1>
</div>
<div align="center">
<strong>Let's see if the strong text works...</strong><br />
<br />
<em>next the slanty text...</em>
</div>
<div align="center">

</div>

<div align="center">
This is an R HTML document. When you click the <b>Knit HTML</b> button a web page will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:</div>
<div align="center", style="color:#000000">
```{r out.width = 4, out.height= 3, warning=FALSE, message=FALSE, echo=FALSE}
library(xtable)
data(tli)
tli.table <- xtable(tli[1:10,])
digits(tli.table)[c(2,6)] <- 0
```

```{r out.width = 4, out.height= 3, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
print(tli.table, include.rownames=F, type="html")
```
</div>
<div align="center">
<p>You can also embed plots, for example:</p>
<h2>CRT Results</h2>
</div>
<div align="center">
```{r fig.width=13, fig.height=12, fig.align='center', out.width=1000, out.height=800, warning=FALSE, message=FALSE, echo=FALSE}
if(nrow(statescore.graph) > 0) plot(statescore.plot) else print("No grades were tested for the 2012-13 Academic Year")
```
</div>
<div align="center">
<h2>MAP Results GO.</h2>
</div>
<div align="center">
```{r fig.width=13, fig.height=12, fig.align='center', out.width=1000, out.height=800, warning=FALSE, message=FALSE, echo=FALSE}
if(nrow(quartile.graph) > 0) plot(quartile.plot) else print("No grades were tested for the 2012-13 Academic Year")
```
</div>
</body>
</html>
